Active Learning from Blackbox to Timed Connectors

### 2016-01-13 paper/paper.tex
.

To solve this problem, many techniques in model constructing were proposed, for instance in
\cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06}.

\todo{finish this part!}

@@

\section{Preliminaries} 
\label{sec:preliminaries}
\subsection{Reo Coordination Language} 
\label{sec:reo}
We provide here a brief overview of the main concepts of Reo, more details can be found in
\cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.

@@

As an extension of \emph{finite state machine}, Mealy machine was first proposed by George. H. Mealy
in \cite{George1955A}. Compared with other variants, Mealy machines are designed to model
reactive systems, where outputs are determined not only by its current state but also the current
inputs. Besides, Mealy machines are supposed to be \emph{input enabled}, which means that all
possible inputs should be acceptable in all states. In other words, if an input is invalid for some
state, we need to manually use an additional state to describe such exceptions.

@@

\todo{supplementation}

>>>>

As a branch of \emph{machine learning} technique, active learning directly applies queries to a
low-level blackbox model and construct hypothesis according to the results.
There're already several works like \cite{DBLP:journals/mt/Daelemans10,
DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06} where active learning is used to extract
\emph{finite state automatas} or \emph{grammars}.

We present \emph{Parameterized Mealy machine} provide a parametierized semantics for timed Reo
channels, which enables us to generate Mealy machines with a given alphabet. Then the $L*$ algorithm
is adapted and optimized to handle Mealy machines with time action.

@@

\section{Preliminar ies} 
\label{sec:preliminaries}
\subsection{Reo Coordination Language} 
\label{sec:reo}
We provide here a brief overview of the main concepts of Reo, more details can be found in
\cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.

@@

In this paper, we use \emph{Mealy machine} to model SUTs.
As an extension of \emph{finite state machine}, Mealy machine was first proposed by George. H. Mealy
in \cite{George1955A}. Compared with other variants, Mealy machines are designed to model
reactive systems, where outputs are determined not only by its current state but also the current
inputs. Besides, Mealy machines are supposed to be \emph{input enabled}, which means that all
possible inputs should be acceptable in all states. In other words, if an input is invalid for some
state, we need to manually use an additional state to describe such exceptions.

@@

We say that a Mealy machine is \emph{finite} if the set $S$ of states and the set $I$ of inputs are
finite. Hereinafter, Mealy machines are always supposed to be finite.

A Mealy machine is in some state $q\in S$ is always ready for inputs at any time. If an input symbol
$i\in I$ is provided, the Mealy machine generates output $\lambda(q,i)$ and jumps to state
$\delta(q,i)$.
